\documentclass{book}
\usepackage{bbm}
\usepackage{fullpage}

\renewcommand*\descriptionlabel[1]{\hspace\leftmargin$#1$}

\title{Quantitative Proprietary Trading}
\author{Ray Ng}
\begin{document}
\maketitle
\tableofcontents

\input{chapters/c1-volatilitytargeting.tex}
\input{chapters/c2-backtesting.tex}


\chapter{Systematic backtesting}
\label{ch:sysbt}

Chapter~\ref{ch:sysbt} is about the implementation of a generic systematic backtester. Note that at the highest level, the system should basically spit out the trades required for the day. This would be a difference between the target portfolio and the current portfolio. Short of an automated trading strategy, the trader is expected to execute faithfully.  

\section{Data layer}
Here's the vectorized data require and that can be precalculated:

\begin{description}
\item[X_i(t)] $\equiv$ price data at fixed frequency
\item[\sigma_{\mathbbm{I}}] $\equiv$ is the unit risk, meaning how many units to buy per \$1 of risk, where the funding units is arbitrary. 
\item[fx_{i}(t)] $\equiv$ is the fx conversion rate from asset price numeraire to funding numeraire example JPY to USD.
\item[\Delta PL_{i}(t) \equiv \left(X_{i}(t+1)-X_i(t)\right)] is the daily PL in [DOM] units for longing one unit of $i$
\item[\Delta PL_{i,\$}(t) \equiv \Delta PL_{i}(t)fx_{i}(t)] is the daily PL in [\$] units for longing one unit of $i$
\item[\Delta PL_{i,C}(t) \equiv \left( r_{FOR}- r_{DOM} \right)\delta t] is the carry earned for longing one unit of $i$
\item[\vec{\delta X}(t) \equiv \vec{X}^{bid}(t) -  \vec{X}^{ask}(t)] is the bid ask spread for the portfolio per unit asset traded]
\item[\vec{\Delta PL}_{tcost}(t) = \vec{N}_{rebalance}(t)\circ \vec{\delta X}(t)/2 \circ \vec{fx}(t).]
\end{description}

\section{Portfolio backtest}
Assuming we had a time series of target inventory: $\vec{N}(t)$, then we can compute the daily PL of the portfolio without transaction costs:
\begin{equation}
\vec{\Delta PL}(t) = \vec{N}(t-1) \circ \vec{\Delta PL (t)} 
\end{equation}
and the portfolio PL is simply given by:
\begin{equation}
\Delta PL (t) = \vec{\Delta PL}(t) \circ \vec{\mathbbm{1}}
\end{equation}
If we wish to include transaction costs, we need to assume rebalance flow. 
\begin{equation}
\vec{N}_{rebalance}(t) = \vec{N(t-1)} - \vec{N(t)}.
\end{equation}
then the rebalance transaction cost can be estimated as:
\begin{equation}
\vec{\Delta PL}_{tcost}(t) = \vec{N}_{rebalance}(t)\circ \vec{\delta X}(t)/2 \circ \vec{fx}(t).
\end{equation}
The full daily PL is then given by:
\begin{equation}
\vec{\Delta PL}_{tcost}(t) = \vec{N}_{rebalance}(t)\circ \vec{\delta X}(t)/2 \circ \vec{fx}(t).
\end{equation}







\end{document}